### 2014-05-09 abstract.tex
Pass through abstract/intro. Eliminate Mosh

The Remy tool can then be used to probe open questions of Internet
congestion control---e.g., what is the cost of maintaining backwards
compatibility with existing algorithms? Is there a tradeoff between a
protocol's performance now and its ability to adapt to networks of the
future? How easy is it to ``learn'' a network protocol to achieve
desired goals, given a necessarily imperfect model of the networks
where it ultimately will be deployed?

>>>>

The Remy tool can then be used to probe the difficulty of the
congestion control problem itself---how easy is it to ``learn'' a
network protocol to achieve desired goals, given a necessarily
imperfect model of the networks where it ultimately will be deployed?
We found weak evidence of a tradeoff between the breadth of the
operating range of a computer-generated protocol and its performance,
but also that a single computer-generated protocol was able to
outperform existing schemes over a thousand-fold range of link rates.

### 2014-05-09 intro.tex
Pass through abstract/intro. Eliminate Mosh

Over the last three years, my colleagues and I have built a series of
systems to explore this approach.

\subsection{Mosh (2011)}

Mosh is primarily a remote terminal application and is not further
discussed in this dissertation, but its design ideas---maintain an
explicit model at runtime, and pursue a stated objective on behalf of
the user---formed the basis of my subsequent work on
transport-protocol design.

\subsection{Sprout (2012)}

@@

\subsection{Remy (2013--)}

@@

Once we had a computerized protocol designer, we explored using it as
a tool to gain understanding about the problem of congestion control.
How easy is it to ``learn'' a network protocol to achieve desired
goals, given a necessarily imperfect model of the networks where it
ultimately will be deployed? Is there a tradeoff between the
performance of an algorithm now---if optimized for a very specific
network---versus the protocol's ability to perform adequately as the
network evolves? What is the cost of compatibility with existing TCP
congestion-control mechanisms? Our experimentation into these
questions of ``learnability'' is reported in
Chapter~\ref{chap:learnability}.

>>>>

Over the last three years, my colleagues and I built a series of
systems that demonstrate the benefits of automated, objective-driven
protocol design.

\subsection{Sprout}

@@

\subsection{Remy}

@@

Once we had a computerized protocol designer, we explored using it as
a tool to gain understanding about the problem of congestion control.
How easy is it to ``learn'' a network protocol to achieve desired
goals, given a necessarily imperfect model of the networks where it
ultimately will be deployed? Is there a tradeoff between the
performance of an algorithm now---if optimized for a very specific
network---versus the protocol's ability to perform adequately as the
network evolves? What is the cost of compatibility with existing TCP
congestion-control mechanisms?

Our research into these questions is reported in
Chapter~\ref{chap:learnability}. We found weak evidence of a tradeoff
between the breadth of the operating range of a computer-generated
protocol and its performance, but also that a single
computer-generated protocol was able to outperform existing schemes
over a thousand-fold range of link rates.

We also measured the benefits and costs of adding ``TCP-awareness'' to
a computer-generated congestion-control protocol protocol. Including
the possibility of TCP cross-traffic in the network model improved
performance when TCP cross traffic was actually present---but hurt
performance when TCP cross traffic was absent, compared with a
``purebred'' protocol designed only to interoperate with itself.

\begin{comment}
\subsection{Mosh}

Mosh is primarily a remote terminal application and is not further
discussed in this dissertation, but its design ideas---maintain an
explicit model at runtime, and pursue a stated objective on behalf of
the user---formed the basis of my subsequent work on
transport-protocol design.
\end{comment}
